\LARGE\textbf{Designing Studies and Evaluating Research Results:\\ Type M and Type S Errors for\\ Pearson Correlation Coefficient }

### 2020-06-01 Documents/Paper_main/Paper_main.Rnw
Add link repo

In the following sections we illustrate how to perform prospective and retrospective design analysis using some examples. We developed two R functions to perform design analysis for Pearson correlation, which are available at the page \todo{…} . The function to perform a prospective design analysis is \texttt{pro\_r()}. It requires as input the plausible effect size (\texttt{rho}), the statistical power (\texttt{power}) the directionality of the test (\texttt{alternative}) which can be set as: “\texttt{two.sided}”, “\texttt{less}” or “\texttt{greate}r” . Type I error rate (\texttt{sig\_level}) is set as default at 5\% and can be changed by the user. The \texttt{pro\_r()} function returns the necessary sample size to achieve the desired statistical power, Type M error rate, the Type S error probability, and the critical value(s) above which a statistically significant result can be found. The function to perform retrospective design analysis is \texttt{retro\_r()}. It requires as input the plausible effect size, the sample size used in the study, and the directionality of the test that was performed. Also in this case, Type I error rate is set as default at 5\% and can be changed by the user.  The function \texttt{retro\_r()} returns the Type M error rate, the Type S error probability, and the critical value(s). For further details regarding the R functions refer to Appendix~\ref{sec:appendix_b}.

@@

To make design analysis accessible to the research community, we provide the R functions to perform prospective design analysis and retrospective design analysis for Pearson correlation coefficient \todo{(link)} together with a short guide on how to use the R functions and a summary of the examples presented in this contribution (Appendix~\ref{sec:appendix_b}).

@@

The code of the functions is available in the file \texttt{Design\_analysis\_r.R} at \todo{add link}.

>>>>

In the following sections we illustrate how to perform prospective and retrospective design analysis using some examples. We developed two R functions to perform design analysis for Pearson correlation, which are available at the page \url{https://osf.io/9q5fr/}. The function to perform a prospective design analysis is \texttt{pro\_r()}. It requires as input the plausible effect size (\texttt{rho}), the statistical power (\texttt{power}) the directionality of the test (\texttt{alternative}) which can be set as: “\texttt{two.sided}”, “\texttt{less}” or “\texttt{greate}r” . Type I error rate (\texttt{sig\_level}) is set as default at 5\% and can be changed by the user. The \texttt{pro\_r()} function returns the necessary sample size to achieve the desired statistical power, Type M error rate, the Type S error probability, and the critical value(s) above which a statistically significant result can be found. The function to perform retrospective design analysis is \texttt{retro\_r()}. It requires as input the plausible effect size, the sample size used in the study, and the directionality of the test that was performed. Also in this case, Type I error rate is set as default at 5\% and can be changed by the user.  The function \texttt{retro\_r()} returns the Type M error rate, the Type S error probability, and the critical value(s). For further details regarding the R functions refer to Appendix~\ref{sec:appendix_b}.

@@

To make design analysis accessible to the research community, we provide the R functions to perform prospective design analysis and retrospective design analysis for Pearson correlation coefficient \url{https://osf.io/9q5fr/} together with a short guide on how to use the R functions and a summary of the examples presented in this contribution (Appendix~\ref{sec:appendix_b}).

@@

The code of the functions is available in the file \texttt{Design\_analysis\_r.R} at \url{https://osf.io/9q5fr/}.
